---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# Introduction

 We have integrated WQS regression into the MI framework in a flexible $\mathcal{R}$ package called **miWQS** to meet a wide variety of needs (Figure \ref{fig::decide}). The data used in this package consist of a mixture of correlated components that share a common outcome while adjusting for other covariates. The correlated components in the set, $X$, may be complete or interval-censored between zero and low thresholds, or detection limits, that may be different across the components. The common outcome, $y$, may be modeled as binary, continuous, count-based, or rate-based and can be adjusted by the `family` and `offset` arguments of `estimate.wqs()`. Additional covariates, $\boldsymbol{Z}$, may be used in the bootstrap imputation and WQS models. 
 If $X$ is interval-censored, the choice of the imputation technique depends on the majority vote of BDL values among the components  [@hargartenAccountingUncertaintyDue2019]. When most chemicals have 80% of its values BDL, we suggest to use the BDLQ1 approach [@hargartenAccountingUncertaintyDue2019]. When most chemicals have less than 80% of its values BDL, the user should perform Bayesian or bootstrapping multiple imputation [@hargartenAccountingUncertaintyDue2019]. Previous literature suggests to ignore any chemicals that have greater than 80% of its values BDL.  [@helselStatisticsCensoredEnvironmental2012, p.93; @bolksBaselineAssessmentLeft2014, p.14] . The **miWQS** package, though, still allows the user to perform single imputation. Regardless of the technique used, researchers may use the **miWQS** package in order to detect an association between the mixture and the outcome and to identify the important components in that mixture.
 

```{r fig.decide, fig.cap="\\label{fig::decide} A decision tree to help researchers in using the miWQS package. The package is flexible and can meet a wide range of needs.", fig.pos = "ht", echo=FALSE,  eval = FALSE}
knitr::include_graphics("figure-word/Decision_Tree_In_Using_miWQS_Package.pdf")
# previously it was .png but picture quality was poor.
```

## Installation

You can install the released version of miWQS from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("miWQS")
```

## Example

Please see the vignette for a detailed step-by-step guide in using this package.
